Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-26 demystify.tex
updates

\part{Appendices}\label{part:appendices}
\appendix
\chapter{Glossary}\label{sec:glossary}

@@

@@

\chapter{Visa for International Students}\label{sec:visa}

>>>>

\part{Appendices}\label{part:appendices}
\appendix
\chapter{Glossary}\label{chap:glossary}

@@

  \item[International vs. Domestic students] International students are loosely defined as those who would need a visa to study in the US (\autoref{chap:visa}). Domestic students (\autoref{sec:domestic-students}) are those who do not need a visa, typically US citizens or permanent residents.

@@

\chapter{Visa for International Students}\label{chap:visa}
